Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-11-27 patchy-review-responses.tex

% \documentclass{article}
% \usepackage{fullpage}
% \input{review-response-commands}
% 
% \begin{document}

\section*{From the editor}

\begin{minipage}[b]{2.5in}
  Resubmission Cover Letter \\
  {\it PLoS Genetics}
\end{minipage}
\hfill
\begin{minipage}[b]{2.5in}
    Molecular and Computational Biology\\
    University of Southern California, \\
    \emph{and} Evolution and Ecology\\
    University of California at Davis\\
  \today
\end{minipage}

@@

\noindent
{\bf To the Editor(s) -- }

\vskip 1em

\begin{quote}
  As can you see from the reviews, two general points were raised by all
  reviewers and I feel that thoroughly addressing both of these points poses a
  prerequisite for further consideration of the manuscript:

  (i) There needs to be some sort of numerical verification (e.g. with
  individual-based simulations) to test the main conclusions, check their
  robustness, and identify the parameter ranges for which they hold.
\end{quote}

We have done a large number of simulations, and compared the results to the theory;
the main comparison occurs in \ref{fig:sim_times} and figures~\ref{fig:sim_probs};
we have also added in supplementary section \ref{apx:parameter_tables} 
visualizations of the simulations at various parameter values
that we think will help some readers in verifying the assumptions.

\begin{quote}
  (ii) The presentation of the main result needs to be improved. In particular,
  all reviewers feel that the main result can be derived in a simpler and more
  intuitive way. I agree with them that at present the manuscript is overly
  technical and would benefit strongly from a more intuitive derivation of the
  results and discussion of the assumptions under which they hold. The reviewers
  provide detailed suggestions on how this can be achieved.
\end{quote}

We sympathize entirely: we felt the same way ourselves,
and went around in similar circles for quite some time
before settling on the argument given in the first draft.
As suggested by the third reviewer, 
we have opted to move the most difficult part of the argument to the Materials \& Methods,
replacing it in the Results with a more \textit{ad hoc} argument
along the lines of that suggested by the reviewers.
(We do think the more formal argument is more solid, however,
and therefore necessary; as discussed below, various seemingly reasonable arguments
give different answers for subtle reasons.)

Other changes of note are:
\begin{itemize}

  \item Several reviewers pointed out that in approximating $\E[1-(1-p_e)^K] \approx \E[K] p_e$
    we were neglecting the case that $s_m \ll s_p$.
    This omission was pure laziness on our part,
    which we have rectified; see the new equation~\eqref{eqn:twocase_migrate}.

  \item We have also improved our discussion of the limits to the theory.

### 2014-11-27 patchy-selection-paper.tex
more sims

%%%%%%%%%
\subsection{What are we assuming?}
\label{ss:assumptions}

A quick review of the parameter regime we are studying here:
First, we assume that 
\textbf{(a)} each patch is large enough to support a stable population of $B$ alleles
($A^{1/d} > (\sigma/\sqrt{2s_p}) \tan^{-1}(\sqrt{s_m/s_p})$).
Next, in using equation \eqref{eqn:eqfreq}, we assume that 
\textbf{(b)} the inter-patch distance is at least several multiples of the dispersal distance
($R \gg \sigma$),
and that 
\textbf{(c)} local drift is not so strong that the equilibirum frequency is at least approximately attained
($s_m \gg 1/(\rho \sigma^d)$).
We also neglect the time for migration-selection equilibrium to be reached,
which has the effect of over-estimating $\migrate$.

We also assume that migration to a new patch takes place over a number of generations;
if there are sufficient rare, long-distance migration events
that would move between patches in a single hop,
this would require a different analysis.

To test the robustness of our results to the various approximations we used,
we used individual-based simulations on a one-dimensional lattice of 501 demes,
run for 25,000 generations.
More details are given below in \nameref{ss:simulations},
and the number of simulations used and parameter values are given in supplementary tables \ref{stab:mutation_params} and \ref{stab:migration_params}.
To estimate the mean time until adaptation by mutation,
we used one centrally located patch of 99 demes
and a mutation rate of $\mu=10^{-5}$,
and to estimate the mean time until adaptation by migration,
we used two centrally located patches of 99 demes
separated by a varying number of demes,
with one patch initialized to have the $B$ allele at frequency 0.8.
In each case, we measured the ``time to adaptation'' as the amount of time until at least 100 $B$ alleles
were present in the previously unadapted patch.
Figure~\ref{fig:sim_times}
summarizes how the results compare to theory,
excluding parameter combinations where a majority of simulations did not adapt by 25,000 generations
or the patch was not large enough to support a stable population of $B$ alleles.
Supplementary figures \ref{sfig:sim_mutation_times} and \ref{sfig:sim_migration_times}
show all times, 
and depictions of typical simulation runs are shown in supplementary figures
\ref{sfig:} .

The agreement is reasonable for both.
The theoretical value $1/\mutrate$ underestimates the mean time to mutation
by a factor of around 2 that depends increases with $s_m$.
This is to be expected for two reasons:
First, we compute the time to reach 100 $B$ alleles, while theory predicts
the time until the the progenitor of those 100 $B$ alleles arose.
Second, the expression for $\mutrate$ neglects effects near the boundary of the patch,
and the larger $s_m$ is, 
the harder it is for mutations that arise near the edge of the patch to establish.
The theoretical values $1/\migrate$ again has a margin of error of a factor of about 2,
with the exception of the weakest disadvantage off the patch, $s_m=10^{-4}$,
which adapt much more quickly than predicted by theory.
However, these simulations fall outside the region where we expect the model to do well,
since $R < \sigma/\sqrt{s_m} \approx 100$.
A glance at SUPP FIGURE XXX reveals more:
since selection is weaker than Wright's effective neighborhood size ($s_m < 1/2 \rho \sigma \le 1/8000$), 
local drift is stronger than selection,
and local migration-selection balance looks very little like the deterministic equilibirium.

@@

An important point to notice is that effective migration and mutation rates will be on the same order if 
$A \mu \approx 2 s_m \exp(- R \sqrt{2 s_m} / \sigma)$,
where $R$ is the distance between the patches,
and $A$ is the area of the not-yet-adapted patch.
In other words, the migrational analogue of ``mutational influx'' ($\mu \rho A$) 
is $2 \rho s_m \exp(- R \sqrt{2 s_m} / \sigma)$,
which depends fairly strongly on the selective disadvantage $s_m$ between patches.
% Note in particular that if $2 s_m < \mu A$ then migration is always slower than new mutation.
Equivalently, the rates are roughly equal if
$R/\sigma = \log(2 s_m/(A \mu))/\sqrt{2s_m}$,
which gives the critical gap size past which adaptation will be mostly parallel
in terms of selection coefficients, patch size, and mutation rate.

@@

If we take the mutational influx in a patch to be one per 10,000 generations ($\rho A \mu = .0001$)
and the population density to be 1 ($\rho =1$, so $-\log(A\mu)\approx 9.2$)
then adaptation is mostly parallel for patches separated by gaps larger than $R/\sigma > (9.2+\log(2s_m))/\sqrt{2s_m}$.
If the selective pressure is fairly strong (say, $s_m=.05$),
then for convergence to be likely,
the distance between patches must be at least 21.8 times the dispersal distance (i.e.\ $R/\sigma > 21.8$).
If $s_m$ is much smaller, say $s_m = .001$, 
the required distance increases to $R/\sigma > 67$.
On the other hand, if the separation is much smaller than this transitional value, 
then adaptations are likely to be shared between patches.

@@

Taking these approximations at face value, 
and assuming both rates are small, 
the time until the first of the two patches is colonized by the $B$
allele will be approximately exponentially distributed with mean $1/(2
\mutrate)$.
Following this, the time until the second patch is subsequently colonized 
(via either migration or new mutation) 
will be exponentially distributed with mean $1/(\mutrate+\migrate)$.
Both these rates scale linearly with population density ($\rho$) 
and the probability of establishment of a rare allele ($p_e\approx 2 s_b/\xi^2$),
so that the overall time to adaptation is robustly predicted to increase with offspring variance ($\xi^2$)
and decrease with population density and beneficial selection coefficient.
Furthermore, the probability that the second adaptation is a new mutation,
i.e.\ the probability of parallel adaptation, is 
\begin{equation} \label{eqn:parallel_prob}
    \frac{\mutrate}{\mutrate+\migrate(R)} = \frac{ A \mu / (2s_m) }{ A \mu / (2s_m) + \left(R \sqrt{2 s_m} /\sigma \right)^{-(d-1)/2}\exp\left(- \sqrt{2 s_m} R / \sigma \right) },  
\end{equation}
so that the probability of parallel mutation should increase
approximately logistically with the distance between the patches, on the spatial scale $\sigma/\sqrt{s_m}$. \revpoint{2}{13}

@@

\subsection*{Acknowledgements}
We would like to heartily thank Joachim Hermisson for a careful reading of the paper,
and catching the algebra error present in the first version of this paper on the bioRxiv,
and also to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.

@@

%%%%%%%
\section{Parameter values for simulations}
\label{apx:parameter_tables}

@@

@@

% sm=0.1
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/18885-r1-501-sb0.01-sm-0.1-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/56325-r1-501-sb0.01-sm-0.1-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/28432-r1-501-sb0.01-sm-0.1-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.1$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.01
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/43099-r1-501-sb0.01-sm-0.01-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/69787-r1-501-sb0.01-sm-0.01-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/11821-r1-501-sb0.01-sm-0.01-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.01$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.001
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/59611-r1-501-sb0.01-sm-0.001-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/93713-r1-501-sb0.01-sm-0.001-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/29850-r1-501-sb0.01-sm-0.001-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.0001
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/15449-r1-501-sb0.01-sm-1e-04-N1600-pophistory-run}.pdf}
    \includegraphics{{example-sims/5582-r1-501-sb0.01-sm-1e-04-N400-pophistory-run}.pdf}
    \includegraphics{{example-sims/24639-r1-501-sb0.01-sm-1e-04-N25-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

@@

\includereviews

>>>>

%%%%%%%%%
\subsection{A review, and a test, of the assumptions}
\label{ss:assumptions}

A quick review of the parameter regime we are studying here:
First, we assume that 
\textbf{(a)} each patch is large enough to support a stable population of $B$ alleles
($A^{1/d} > (\sigma/\sqrt{2s_p}) \tan^{-1}(\sqrt{s_m/s_p})$).
Next, in using equation \eqref{eqn:eqfreq}, we assume that 
\textbf{(b)} the inter-patch distance is at least the characteristic length
($R > \sigma/\sqrt{s_m}$),
and that
\textbf{(c)} local drift is not so strong that the equilibirum frequency is at least approximately attained
(using Wright's effective neighborhood size, $s_m \gg 1/(\rho \sigma^d)$).
The last requirement is necessary because if the $B$ allele fixes in large neighborhoods where it is deleterious,
we cannot approximate its dynamics via a branching process.
We also neglect the time for migration-selection equilibrium to be reached,
which has the effect of over-estimating $\migrate$,
but don't know a good way to estimate this contribution.
As discussed above, we also assume that migration to a new patch takes place over a number of generations;
if there are sufficient rare, long-distance migration events
that would move between patches in a single hop,
this would require a different analysis.

To test the robustness of our results to the various approximations we used,
we used individual-based simulations on a one-dimensional lattice of 501 demes,
run for 25,000 generations.
More details are given below in \nameref{ss:simulations},
and the number of simulations used and parameter values are given in supplementary tables \ref{stab:mutation_params} and \ref{stab:migration_params}.
To estimate the mean time until adaptation by mutation,
we used one centrally located patch of 99 demes
and a mutation rate of $\mu=10^{-5}$,
and to estimate the mean time until adaptation by migration,
we used two centrally located patches of 99 demes
separated by a varying number of demes,
with one patch initialized to have the $B$ allele at frequency 0.8.
In each case, we measured the ``time to adaptation'' as the amount of time until at least 100 $B$ alleles
were present in the previously unadapted patch.
Figure~\ref{fig:sim_times}
summarizes how the results compare to theory,
excluding parameter combinations where a majority of simulations did not adapt by 25,000 generations
or the patch was not large enough to support a stable population of $B$ alleles.
Supplementary figures \ref{sfig:sim_migration_times} and \ref{sfig:sim_mutation_times} 
show all times, 
and depictions of typical simulation runs are shown in supplementary figures
\ref{sfig:sims_1}, \ref{sfig:sims_2}, \ref{sfig:sims_3}, \ref{sfig:sims_4}, \ref{sfig:sims_5}, \ref{sfig:sims_6}, \ref{sfig:sims_7}, and \ref{sfig:sims_8}.

The agreement is reasonable for both.
The theoretical value $1/\mutrate$ underestimates the mean time to mutation
by a factor of around 2 that depends increases with $s_m$.
This is to be expected for two reasons:
First, we compute the time to reach 100 $B$ alleles, while theory predicts
the time until the the progenitor of those 100 $B$ alleles arose.
Second, the expression for $\mutrate$ neglects effects near the boundary of the patch,
and the larger $s_m$ is, 
the harder it is for mutations that arise near the edge of the patch to establish.
The theoretical values $1/\migrate$ again has a margin of error of a factor of about 2,
with the exception of the weakest disadvantage off the patch, $s_m=10^{-4}$,
which adapt much more quickly than predicted by theory.
However, these simulations fall outside the region where we expect the model to do well,
since $R < \sigma/\sqrt{s_m} \approx 100$.
A glance at supplementary figure \ref{sfig:sims_8} shows more:
since $s_m$ is so small, the second patch is reached by migrants before the migration-selection eqilibrium is reached,
and at migration-selection equilibrium, the two patches act as a single meta-patch.

@@

Let $\gamma = \min(1,s_m/p_e)$.
An important point to notice is that effective migration and mutation rates will be on the same order if 
$A \mu \approx 2 \gamma s_m \exp(- R \sqrt{2 s_m} / \sigma)$,
where $R$ is the distance between the patches,
and $A$ is the area of the not-yet-adapted patch.
In other words, the migrational analogue of ``mutational influx'' ($\mu \rho A$) 
is $2 \rho \gamma s_m \exp(- R \sqrt{2 s_m} / \sigma)$,
which depends fairly strongly on the selective disadvantage $s_m$ between patches.
% Note in particular that if $2 s_m < \mu A$ then migration is always slower than new mutation.
Equivalently, the rates are roughly equal if
$R/\sigma = \log(2 \gamma s_m/(A \mu))/\sqrt{2s_m}$,
which gives the critical gap size past which adaptation will be mostly parallel
in terms of selection coefficients, patch size, and mutation rate.

@@

If we take the mutational influx in a patch to be one per 10,000 generations ($\rho A \mu = .0001$),
$s_m>p_e$ so that $\gamma=1$,
and the population density to be 1 ($\rho =1$, so $-\log(A\mu)\approx 9.2$)
then adaptation is mostly parallel for patches separated by gaps larger than $R/\sigma > (9.2+\log(2s_m))/\sqrt{2s_m}$.
If the selective pressure is fairly strong (say, $s_m=.05$),
then for convergence to be likely,
the distance between patches must be at least 21.8 times the dispersal distance (i.e.\ $R/\sigma > 21.8$).
If $s_m$ is much smaller, say $s_m = .001$, 
the required distance increases to $R/\sigma > 67$.
On the other hand, if the separation is much smaller than this transitional value, 
then adaptations are likely to be shared between patches.

@@

Taking these approximations at face value, 
and assuming both rates are small, 
the time until the first of the two patches is colonized by the $B$
allele will be approximately exponentially distributed with mean $1/(2
\mutrate)$.
Following this, the time until the second patch is subsequently colonized 
(via either migration or new mutation) 
will be exponentially distributed with mean $1/(\mutrate+\migrate)$.
Both these rates scale linearly with population density ($\rho$) 
and the probability of establishment of a rare allele ($p_e\approx 2 s_b/\xi^2$, for $p_e>s_m$),
so that the overall time to adaptation is robustly predicted to increase with offspring variance ($\xi^2$)
and decrease with population density and beneficial selection coefficient.
Furthermore, the probability that the second adaptation is a new mutation,
i.e.\ the probability of parallel adaptation, 
with $\gamma = \min(1,s_m/p_e)$,
is 
\begin{equation} \label{eqn:parallel_prob}
    \frac{\mutrate}{\mutrate+\migrate(R)} = \frac{ A \mu / (2s_m) }{ A \mu / (2s_m) + \gamma \left(R \sqrt{2 s_m} /\sigma \right)^{-(d-1)/2}\exp\left(- \sqrt{2 s_m} R / \sigma \right) },  
\end{equation}
so that the probability of parallel mutation should increase
approximately logistically with the distance between the patches, on the spatial scale $\sigma/\sqrt{s_m}$. \revpoint{2}{13}

@@

\subsection*{Acknowledgements}
We would like to heartily thank Joachim Hermisson for a number of insightful suggestions,
and catching the algebra error present in the first version of this paper on the bioRxiv,
as well as the two anonymous reviewers.
We would also like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.

@@

%%%%%%%
\section{More information about the simulations}
\label{apx:parameter_tables}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mutation-times-predicted}
  \end{center}
  \caption{
    The same data shown in the left panel of figure~\ref{fig:sim_times},
    but all times shown (not just the interquartile ranges),
    and including those parameter values at which most of the simulations did not adapt by 25,000 generations.
  } \label{sfig:sim_migration_times}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{migration-time-predicted}
  \end{center}
  \caption{
    The same data shown in the right panel of figure~\ref{fig:sim_times},
    but all times shown (not just the interquartile ranges),
    and including those parameter values at which most of the simulations did not adapt by 25,000 generations.
    The left panel has the predicted time to adaptation on the horizontal axis as in figure~\ref{fig:sim_times},
    and the right panel has, for comparison, the raw distance between patches 
    (which predicts time to adaptation, but not as well).
  } \label{sfig:sim_mutation_times}
\end{figure}

@@

% sm=0.1
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/18885-r1-501-sb0_01-sm-0_1-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/56325-r1-501-sb0_01-sm-0_1-N600-pophistory-run}
    \includegraphics{example-mutation-sims/28432-r1-501-sb0_01-sm-0_1-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.1$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_1}
\end{figure}

% sm=0.01
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/43099-r1-501-sb0_01-sm-0_01-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/69787-r1-501-sb0_01-sm-0_01-N600-pophistory-run}
    \includegraphics{example-mutation-sims/11821-r1-501-sb0_01-sm-0_01-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.01$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_2}
\end{figure}

% sm=0.001
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/59611-r1-501-sb0_01-sm-0_001-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/93713-r1-501-sb0_01-sm-0_001-N600-pophistory-run}
    \includegraphics{example-mutation-sims/29850-r1-501-sb0_01-sm-0_001-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_3}
\end{figure}

% sm=0.0001
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/15449-r1-501-sb0_01-sm-1e-04-N1600-pophistory-run}
    \includegraphics{example-mutation-sims/5582-r1-501-sb0_01-sm-1e-04-N400-pophistory-run}
    \includegraphics{example-mutation-sims/24639-r1-501-sb0_01-sm-1e-04-N25-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_4}
\end{figure}

% sm=0.1, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/89826-r1-501-sb0_01-sm-0_1-N4000-pophistory-run}
    \includegraphics{example-migration-sims/76178-r1-501-sb0_01-sm-0_1-N1000-pophistory-run}
    \includegraphics{example-migration-sims/97545-r1-501-sb0_01-sm-0_01-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.1$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_5}
\end{figure}

% sm=0.01, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/42080-r1-501-sb0_01-sm-0_01-N4000-pophistory-run}
    \includegraphics{example-migration-sims/82698-r1-501-sb0_01-sm-0_01-N1000-pophistory-run}
    \includegraphics{example-migration-sims/97545-r1-501-sb0_01-sm-0_01-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.01$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_6}
\end{figure}

% sm=0.001, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/88079-r1-501-sb0_01-sm-0_001-N4000-pophistory-run}
    \includegraphics{example-migration-sims/3464-r1-501-sb0_01-sm-0_001-N1000-pophistory-run}
    \includegraphics{example-migration-sims/37774-r1-501-sb0_01-sm-0_001-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_7}
\end{figure}

% sm=0.0001, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/26044-r1-501-sb0_01-sm-1e-04-N4000-pophistory-run}
    \includegraphics{example-migration-sims/85750-r1-501-sb0_01-sm-1e-04-N1000-pophistory-run}
    \includegraphics{example-migration-sims/4111-r1-501-sb0_01-sm-1e-04-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.0001$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_8}
\end{figure}

@@

%%%% Reviews
\includereviews
